Vaccination

### 2022-03-07 code/vaccination-indicators.Rmd
update for git

---
title: "Vaccination"
author: "FD"
output: 
  html_document:
      self_contained: no

---

@@

```{r results = 'hide'}
# Functions to discretize the data
source("1_functions-quantiles.R")
# `discretizeQ`

@@

vv <- dat.all[, "Unemployment_Benef"]
plot(discretizeQ(vv, seq(0, 1, 0.1)), 
     discretizeQ(vv, seq(0, 1, 0.5)))

>>>>

---
title: "Vaccination"
author: "FD"
output:
  html_document:
    self_contained: no
    keep_md: true
    toc: true
    toc_float: true
  pdf_document: default
---

@@

```{r results = 'hide', fig.show='hide'}
# Functions to discretize the data
source("1_functions-quantiles.R")
# `discretizeQ`

@@

#vv <- dat.all[, "Unemployment_Benef"]
#plot(discretizeQ(vv, seq(0, 1, 0.1)), 
#     discretizeQ(vv, seq(0, 1, 0.5)))
